\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-29 paper/ms.tex
Fix cite; minor tweaks

% to-do list
% ----------
% - Fit summary in the first page.

@@

The surface lithium abundance is the only indicator of a
younger age.
If the two stars were only several hundred Myrs old, then they would likely
have been part of a larger comoving group of stars.
However, there is no evidence in our search\cite{2017AJ....153..257O} of
comoving pairs using \tgas\ that these stars belong to a larger group of
young stars.
Very young stars often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks (\todo{needs refernces}).
We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars, and
found no evidence for indications of activity or infrared excess in their
spectral energy distributions (\figname~\ref{fig:sed}).
The low $v\sin(i)$ values (\tablename~\ref{tab:t1}) also argue against very
young ages that would be inferred from the surface lithium abundances.
Finally, we computed the Galactic orbit of the pair using the median of the
posterior sample over the phase space coordinates of \sunanalog, in a Milky
Way-like gravitational potential\cite{Bovy:2015} using \project{Gala}\cite{gala}.
The pair's fiducial orbit has a vertical action larger than the Sun, favoring
an older age (\citealt{Wielen:1977,Aumer:2016}); see \figname~\ref{fig:orbit}.
We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
old main sequence stars, and that their unusually high \elem{Li} abundance
requires an alternative explanation; our favored explanation being the accretion
of rocky material that has locked lithium.

@@

We stress that while the calculation carried out is useful in
an order-of-magnitude sense, further investigation of each of the simplifying
assumptions made is warranted.
In addition, the composition of bulk Earth has some uncertainties.
For example, the reported bulk Earth concentration of \elem{Mn}, varies from
$800$ to $1700$~ppm\cite{1998psc..book.....L,mcdonough2001composition,2003TrGeo...2..547M}
largely due to uncertainties in the composition of the Earth's core.
Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}
\elem{Li} for \bizarreone\ is remarkable.

>>>>

% to-do list
% ----------
% - Add items here.

@@

The surface lithium abundance is the only indicator of a
younger age.
If the two stars were only several hundred Myrs old, then they would likely
have been part of a larger comoving group of stars.
However, there is no evidence in our search\cite{2017AJ....153..257O} of
comoving pairs using \tgas\ that these stars belong to a larger group of
young stars.
Very young stars often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks.
We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars, and
found no evidence for indications of activity or infrared excess in their
spectral energy distributions (\figname~\ref{fig:sed}).
The low $v\sin(i)$ values (\tablename~\ref{tab:t1}) also argue against very
young ages that would be inferred from the surface lithium abundances.
Finally, we computed the Galactic orbit of the pair using the median of the
posterior sample over the phase space coordinates of \sunanalog, in a Milky
Way-like gravitational potential\cite{Bovy:2015} using \project{Gala}\cite{gala}.
The pair's fiducial orbit has a vertical action larger than the Sun, favoring
an older age\cite{Wielen:1977,Aumer:2016} (\figname~\ref{fig:orbit}).
We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
old main sequence stars, and that their unusually high \elem{Li} abundance
requires an alternative explanation; our favored explanation being the accretion
of rocky material that has locked lithium.

@@

We stress that while the calculation carried out is useful in
an order-of-magnitude sense, further investigation of each of the simplifying
assumptions made is warranted.
In addition, the composition of bulk Earth has some uncertainties.
For example, the reported bulk Earth concentration of \elem{Mn}, varies from
$800$ to $1700$~ppm\cite{1998psc..book.....L,mcdonough2001composition,2003TrGeo...2..547M}
largely due to uncertainties in how much \elem{Mn} is in the Earth's core.
Given these limitations, the level of agreement for $\Delta\elemH{X}$ {\it and}
\elem{Li} for \bizarreone\ is remarkable.
